---
title: "Errata for *A 2 million-person, campaign-wide field experiment shows how digital advertising affects voter turnout*"
format:
  pdf:
    output-file: aggarwal_etal_2023_errata.pdf
    toc: false
    number-sections: false
    geometry: margin=1in
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
here::i_am("errata.qmd")

gt <- read_csv(
  here::here("ground_truth", "aggarwal_etal_2023_ground_truth.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
extraction <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), needs_block = col_logical(),
                   .default = col_guess())
)

# claim_id is never missing here, but indexing with a bare logical would return
# extra NA elements the moment one were, so every lookup asserts a single row.
value <- function(id, column = "value_rewrite") {
  row <- gt[!is.na(gt$claim_id) & gt$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row[[column]]
}

published <- function(id) {
  row <- extraction[extraction$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row$value_paper
}

number_word <- function(x) {
  words <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
             "ten", "eleven", "twelve", "thirteen", "fourteen", "fifteen", "sixteen",
             "seventeen", "eighteen", "nineteen", "twenty", "twenty-one", "twenty-two",
             "twenty-three", "twenty-four")
  words[as.integer(x)]
}

with_commas <- function(x) format(round(as.numeric(x)), big.mark = ",", scientific = FALSE)

# Monthly persuasion spending, from the figure the sentence describes.
monthly_spend <-
  read_csv(here::here("maintained", "output", "figure_b2_acronym_spending.csv"),
           show_col_types = FALSE) |>
  filter(panel == "Keyword") |>
  group_by(month) |>
  summarize(spend_lb = sum(spend_lb), .groups = "drop") |>
  arrange(desc(spend_lb))

top_month <- format(monthly_spend$month[1], "%B")
top_spend <- with_commas(monthly_spend$spend_lb[1])
july_spend <- with_commas(monthly_spend$spend_lb[monthly_spend$month == as.Date("2020-07-01")])

n_covariates <- value("methods_n_covariates")
n_covariates_word <- number_word(n_covariates)

audience <- with_commas(published("methods_treatment_audience"))
eligible <- with_commas(published("methods_programme_eligible"))

omnibus_num_df <- value("methods_omnibus_df_first_subscript")
omnibus_den_df <- format(round(value("methods_omnibus_df_second_subscript")), scientific = FALSE)
omnibus_den_df_commas <- with_commas(value("methods_omnibus_df_second_subscript"))
omnibus_f <- sprintf("%.4f", value("methods_omnibus_f"))
omnibus_p <- sprintf("%.3f", value("methods_omnibus_p"))

wesleyan_share <- sprintf("%.2f", value("si_c_wesleyan_share"))
wesleyan_total <- with_commas(published("si_c_wesleyan_total"))
wesleyan_acronym <- with_commas(published("si_c_wesleyan_acronym"))
```

```{r}
#| label: entries
#| include: false

# THE ERRATA SPINE. Every entry is defined once, here, and rendered from this tibble into
# this document and into the machine-readable errata_entries.csv written at the bottom of
# the file, which is what any other document carrying these corrections reads. Before the
# spine existed an entry was written out in prose wherever it was needed, and the copies
# had already diverged.
#
# [[...]] marks the span that changes. Each renderer supplies its own markup for it: bold
# here. Nothing else in a field is markup, so the same string can be set by any of them.
#
# Numbering is the published note's and is APPEND-ONLY: entry 3 can already have been cited,
# so a later finding is added at the end and never interleaved.
#
# A published or corrected value that the pipeline computes stays computed: the field is
# built with str_glue() so the number is produced when this document renders, not typed.
#
# claim_ids is the semicolon-separated list of ground-truth claim_id values the entry
# corrects, and it is what makes "is this finding published?" a query rather than a reading
# of every note. It is empty where an entry has no ground-truth row, which is normal for a
# bibliographic or structural entry. ground_truth/build_ground_truth.R refuses to build if
# any id here is absent from the ground truth.
entries <- tribble(
  ~entry, ~class, ~source, ~form, ~title, ~location, ~published, ~corrected, ~note, ~claim_ids,

  1, "label", "pipeline", "full",
  "The month of heaviest persuasion spending",
  "published SI section C, p. 8",
  "In fact, we observe significant early spending (Acronym spent more on persuasion in [[July]] than in any other month, see main Figure [[??]]), and we find much stronger effects on early voting than day of voting (see Figure 3 in the main text).",
  str_glue("In fact, we observe significant early spending (Acronym spent more on persuasion in [[{top_month}]] than in any other month, see [[Supplementary Figure 2]]), and we find much stronger effects on early voting than day of voting (see Figure 3 in the main text)."),
  str_glue(
    "The figure the sentence points at is Supplementary Figure 2, whose two panels split ",
    "Acronym's monthly lower-bound spending on persuasion advertisements by format and by ",
    "keyword. Summed over either panel's series, the largest month is {top_month} 2020 at ",
    "US\\${top_spend}, against US\\${july_spend} in July. The cross-reference did not resolve ",
    "when the document was typeset. The sentence's argument, that Acronym spent heavily ",
    "earlier in the campaign than other left-leaning advertisers did, is unaffected: ",
    "{top_month} is earlier than July."),
  "si_c_july_highest_spend;si_c_broken_cross_reference",

  2, "quantity", "pipeline", "full",
  "The number of pre-treatment covariates tested for balance",
  "published Methods, p. 6",
  # THE QUOTATION ENDS WHERE THE PAGE'S SENTENCE DOES NOT. Published Methods
  # p. 6 reads "... only two exhibited statistically significant imbalance:
  # Trump support score (t ...", with a colon and the two named. Quoting it
  # with a full stop made the passage a string that occurs nowhere in the
  # article, so the remastered edition's matcher found nothing and skipped the
  # correction in silence while this note went on advertising it.
  #
  # It stops at "covariates" rather than at "imbalance" because of what comes
  # next. The sentence runs straight into two inline statistics whose estimator
  # hats the published text layer sorts out of their own clauses, so the
  # remastered edition exempts that whole run from its comparison, and the
  # exemption has to be anchored on the last clean prose before the damage,
  # which is this sentence's own tail. A quotation reaching into it cannot be
  # found on either side. The explanation below is what carries the rest of the
  # sentence to a reader.
  "As shown in Fig. 5, the random assignment procedure generated treatment and control groups that were balanced on pre-treatment characteristics in this subset. Out of [[21]] covariates",
  str_glue("As shown in Fig. 5, the random assignment procedure generated treatment and control groups that were balanced on pre-treatment characteristics in this subset. Out of [[{n_covariates}]] covariates"),
  str_glue(
    "Figure 5 plots {n_covariates_word} covariates and Supplementary Table 3 prints ",
    "{n_covariates_word} rows. The count of two significant imbalances is right, and so is ",
    "everything the paragraph goes on to say about them."),
  "methods_n_covariates",

  3, "quantity", "pipeline", "full",
  "The size of the treatment audience",
  "published Methods, p. 7",
  str_glue("The full cost of the advertising campaign was US\\$8.9 million, spread out over a treatment audience of [[{audience} million]] ({eligible} programme-eligible voters × our 60% match rate), amounting to US\\$4.46 of advertising expenditure per voter."),
  str_glue("The full cost of the advertising campaign was US\\$8.9 million, spread out over a treatment audience of [[{audience}]] ({eligible} programme-eligible voters × our 60% match rate), amounting to US\\$4.46 of advertising expenditure per voter."),
  str_glue(
    "The parenthetical states the arithmetic: {eligible} times a 60 per cent match rate is ",
    "{audience} people. The word \"million\" makes the figure a million times too large."),
  "methods_treatment_audience_scale",

  4, "quantity", "pipeline", "full",
  "The degrees of freedom of the balance F test",
  "published Methods, p. 6",
  str_glue("An F-test comparing a regression of treatment status on covariates with strata fixed effects versus a restricted model predicting treatment status from strata fixed effects was non-significant (F~[[{published('methods_omnibus_df_first_subscript')},−18]]~ = {omnibus_f}; P = {omnibus_p})."),
  str_glue("An F-test comparing a regression of treatment status on covariates with strata fixed effects versus a restricted model predicting treatment status from strata fixed effects was non-significant (F~[[{omnibus_num_df},{omnibus_den_df}]]~ = {omnibus_f}; P = {omnibus_p})."),
  str_glue(
    "An F statistic carries its numerator degrees of freedom first. The unrestricted model ",
    "has {omnibus_num_df} more parameters than the restricted one and leaves ",
    "{omnibus_den_df_commas} residual degrees of freedom. The published subscripts are the ",
    "second row of the Wald test's printed output, where the first figure is that model's ",
    "residual degrees of freedom and the second is the difference in parameters, printed as ",
    "a negative number. The statistic and the p-value are right."),
  "methods_omnibus_df_first_subscript;methods_omnibus_df_second_subscript",

  5, "quantity", "pipeline", "full",
  "Acronym's share of federal advertising spending on Facebook",
  "published SI section C, p. 5",
  str_glue("According to this data, there was a total of approximately \\${wesleyan_total} spent on federal races on Facebook from 2/1/2020 to 11/3/2020, \\${wesleyan_acronym} ([[0.67%]]) of which was from Acronym."),
  str_glue("According to this data, there was a total of approximately \\${wesleyan_total} spent on federal races on Facebook from 2/1/2020 to 11/3/2020, \\${wesleyan_acronym} ([[{wesleyan_share}%]]) of which was from Acronym."),
  str_glue(
    "A rounding artifact rather than a substantive error: the quotient of the sentence's own ",
    "two figures is {sprintf('%.4f', value('si_c_wesleyan_share'))} per cent, which rounds ",
    "up. The share is kept at two decimal places because at one decimal the published and ",
    "corrected figures are the same."),
  "si_c_wesleyan_share",

  # Entries 6 and 7 are the same defect twice and are kept apart because they
  # lose two different variables. The randomisation listing in section E is set
  # at a measure wider than the page, and two of its lines are drawn past the
  # right edge: the text layer ends where the drawing does, so nothing is
  # recoverable from the published page. Each loses the whole of its
  # `then ... end as ...` clause, which is the definition of the variable.
  # Found by measuring every line's extent against the page width while the
  # remastered edition's section E was being set, not by reading.
  6, "definition", "remaster", "full",
  "The definition of the black variable in the randomisation code",
  "published SI section E, p. 15",
  ", case when vb_voterbase_race = ’African-American’ or (vb_voterbase_race = ’Uncoded’ and [[civis_race]]",
  ", case when vb_voterbase_race = ’African-American’ or (vb_voterbase_race = ’Uncoded’ and [[civis_race = ’AFAM’) then ’black’ else null end as black]]",
  paste(
    "The line is drawn to x 610.6 on a page 612 points wide and the text layer",
    "ends with `civis_race`. The complete line is in the authors' own",
    "`Acronym/notes/gh_randomization_sql.mssql`, line 17, which agrees with every",
    "other line of the published listing except for the capitalisation of the",
    "schema name. `black` is one of the two race categories the Methods report as",
    "no longer available, and the code as printed cannot be run."),
  "si_e_sql_black_definition",

  7, "definition", "remaster", "full",
  "The definition of the hispanic variable in the randomisation code",
  "published SI section E, p. 15",
  ", case when vb_voterbase_race = ’Hispanic’ or (vb_voterbase_race = ’Uncoded’ and [[civis_race = ’HISPA]]",
  ", case when vb_voterbase_race = ’Hispanic’ or (vb_voterbase_race = ’Uncoded’ and [[civis_race = ’HISPANIC’) then ’hispanic’ else null end as hispanic]]",
  paste(
    "The line is drawn to x 615.8 on a page 612 points wide, so it ends beyond the",
    "page edge and mid-token, at `’HISPA`. The complete line is in the authors' own",
    "`Acronym/notes/gh_randomization_sql.mssql`, line 18. `hispanic` is the other",
    "race category the Methods report as no longer available."),
  "si_e_sql_hispanic_definition"
) |>
  mutate(across(c(title, published, corrected, note), as.character))

stopifnot(nrow(entries) == max(entries$entry), !anyDuplicated(entries$entry))

# Every id an entry claims to correct must be a real ground-truth claim. The build gate in
# ground_truth/build_ground_truth.R checks the same property from the other side; checking it
# here too means a dangling id cannot survive a render.
cited_ids <- entries$claim_ids |>
  str_split(";") |>
  unlist() |>
  str_trim() |>
  discard(\(x) is.na(x) | x == "")
stopifnot(all(cited_ids %in% gt$claim_id))

# The spine's markup, resolved for this document.
bold <- function(x) str_replace_all(x, "\\[\\[(.*?)\\]\\]", "**\\1**")
```

`r str_to_title(number_word(nrow(entries)))` corrections to *Nature Human Behaviour* article
`r "10.1038/s41562-022-01487-4"`. None of
them changes a conclusion of the article. Every corrected value below is computed at render time
from a full reproduction of the published analysis, held in the repository
`active-maintenance-aec/aggarwal_etal_2023`. Bold marks the tokens that changed; everything else
in each corrected sentence is the published wording.

```{r}
#| label: render-entries
#| echo: false
#| results: asis

# A heading is only a heading when a blank line precedes it, so every entry opens with one.
walk(seq_len(nrow(entries)), function(i) {
  e <- entries[i, ]
  cat("\n\n## ", e$entry, ". ", e$title, "\n\n> ", bold(e$published),
      "\n\n**Corrected:** ", bold(e$corrected), "\n\n", e$note, "\n", sep = "")
})
```

```{r}
#| label: emit-spine
#| include: false

# The machine-readable spine, written wherever this document is rendered. Anything else that
# carries these corrections reads it rather than keeping its own copy, so the two cannot drift.
write_csv(entries, here("errata_entries.csv"))
```
