---
title: "Maintained reproduction of Aggarwal, Allen, Coppock, Frankowski, Messing, Zhang, Barnes, Beasley, Hantman and Zheng (2023)"
format:
  gfm:
    output-file: README.md
    toc: true
  pdf:
    output-file: aggarwal_etal_2023_report.pdf
    toc: true
    number-sections: true
---

```{r}
#| label: setup
#| include: false
library(tidyverse)
library(here)
library(knitr)
here::i_am("README.qmd")

latex_out <- knitr::is_latex_output()
options(width = 200)

gt <- read_csv(
  here::here("ground_truth", "aggarwal_etal_2023_ground_truth.csv"),
  col_types = cols(value_paper = col_character(), .default = col_guess())
)
coverage <- read_csv(here::here("ground_truth", "float_coverage.csv"),
                     show_col_types = FALSE)
run_status <- read_csv(here::here("ground_truth", "archive_run_status.csv"),
                       show_col_types = FALSE)
overwrites <- read_csv(here::here("ground_truth", "archive_overwrites.csv"),
                       show_col_types = FALSE)
write_calls <- read_csv(here::here("ground_truth", "archive_write_calls.csv"),
                        show_col_types = FALSE)
manifest <- read_csv(here::here("original_manifest.csv"), show_col_types = FALSE)
extraction <- read_csv(
  here::here("ground_truth", "published_claims.csv"),
  col_types = cols(value_paper = col_character(), needs_block = col_logical(),
                   .default = col_guess())
)
appendix_cells <- read_csv(here::here("ground_truth", "published_appendix_values.csv"),
                           col_types = cols(value_paper = col_character(),
                                            .default = col_guess()))
maintext_cells <- read_csv(here::here("ground_truth", "published_maintext_tables.csv"),
                           col_types = cols(value_paper = col_character(),
                                            .default = col_guess()))
descriptive <- read_csv(here::here("maintained", "output", "text_descriptive_claims.csv"),
                        show_col_types = FALSE)

# The errata spine, defined once in errata.qmd and written out by it. This section reads it
# rather than keeping its own count, so the two cannot disagree about how many entries there
# are.
spine <- read_csv(here::here("errata_entries.csv"), show_col_types = FALSE)
n_errata_word <- c("one", "two", "three", "four", "five", "six", "seven", "eight", "nine",
                   "ten", "eleven", "twelve")[nrow(spine)]

# claim_id is never missing in this ground truth, but indexing it with a bare
# logical would return extra NA elements the moment one were, so every lookup
# goes through an accessor that asserts a single row.
value <- function(id, column = "value_rewrite") {
  row <- gt[!is.na(gt$claim_id) & gt$claim_id == id, ]
  stopifnot(nrow(row) == 1)
  row[[column]]
}

pass <- function(name) run_status |> filter(pass == name)

with_commas <- function(x) format(round(as.numeric(x)), big.mark = ",", scientific = FALSE)

show_table <- function(x, caption = NULL) {
  if (latex_out) {
    knitr::kable(x, caption = caption, booktabs = TRUE, linesep = "") |>
      kableExtra::kable_styling(latex_options = c("striped", "scale_down"))
  } else {
    knitr::kable(x, caption = caption)
  }
}

figure <- function(stem) {
  extension <- if (latex_out) ".pdf" else ".png"
  knitr::include_graphics(file.path("maintained", "output", paste0(stem, extension)))
}

published_numbers_total <- nrow(appendix_cells) + nrow(maintext_cells)
```

*Drafted by Claude Opus 5 under the supervision of Alex Coppock.*

## What this repository is

This repository re-runs the analysis behind a published article from its deposited data, in
current R, and lays every number the article prints against what that analysis produces. It holds
three things: a script that fetches and verifies the authors' replication archive, a rewrite of
the analysis using current packages, and a ground truth that records, claim by claim, whether the
published number reproduces.

| | |
|---|---|
| Article | Aggarwal M, Allen J, Coppock A, Frankowski D, Messing S, Zhang K, Barnes J, Beasley A, Hantman H and Zheng S (2023). "A 2 million-person, campaign-wide field experiment shows how digital advertising affects voter turnout." *Nature Human Behaviour* 7, 332--341. <https://doi.org/10.1038/s41562-022-01487-4> |
| Replication archive | <https://doi.org/10.7910/DVN/YMKVA1> |
| Pre-analysis plans | <https://osf.io/3evfp> and <https://osf.io/jkush> |
| Treatment stimuli | <https://osf.io/ex3kq> |

### Folder layout

```
download_original.R    fetches and verifies the deposited archive
run_all.R              runs everything, in order
original/              the deposited archive (not redistributed; fetched on demand)
original_manifest.csv  every deposited file, its size and its published checksum
maintained/            the rewrite; maintained/output/ holds every number it produces
ground_truth/          the extraction, the comparison and the gates
errata.qmd             corrections to the published article
```

### How to reproduce

Download the repository, open `aggarwal_etal_2023.Rproj`, and run:

```r
source("run_all.R")
```

`run_all.R` fetches the deposited archive from Harvard Dataverse, verifies every file against its
published checksum and byte size, writes every figure and table, computes every in-text quantity,
runs the deposited scripts in a scratch copy, rebuilds the ground truth and re-verifies the
archive. Nothing writes into `original/`. The archive is
`r sprintf("%.0f", sum(manifest$bytes) / 1e6)` MB, most of it one Facebook Ad Library extract, so
the first run spends several minutes downloading.

## The paper

A campaign-level field experiment run by Acronym, a left-leaning non-profit, during the 2020 US
presidential election. Of the registered voters in Arizona, Michigan, North Carolina,
Pennsylvania and Wisconsin who met the campaign's targeting criteria, a randomly sampled holdout
saw none of Acronym's advertising for eight months while everyone else saw the full programme.
Turnout was then read from the TargetSmart voter file for the
`r with_commas(value("methods_n_analysis_sample"))` participants whose assignment could be
recovered.

The headline results are an average effect on turnout indistinguishable from zero and a
difference in conditional average treatment effects by modelled Trump support of
`r sprintf("%.1f", value("abstract_dic"))` percentage points: turnout rose
`r sprintf("%.1f", value("abstract_biden_effect"))` points among Biden leaners and fell
`r sprintf("%.1f", value("abstract_trump_effect"))` points among Trump leaners.

## Does the deposited archive run?

The deposit is `r nrow(manifest)` files: eleven analysis scripts, four data files and a README.
Every script was run in a scratch copy, twice, once as the archive ships and once stripped to
data plus code.

```{r}
#| label: archive-run
#| echo: false
run_status |>
  count(pass, outcome) |>
  pivot_wider(names_from = outcome, values_from = n, values_fill = 0) |>
  show_table(caption = "Deposited scripts by pass and outcome.")
```

The two passes give the same answer, and that is a finding rather than an omission. Stripping the
copy to data plus code removes nothing, because no deposited file is written by any deposited
script: the write-call scan below returns `r nrow(write_calls)` uncommented writes and all
`r nrow(write_calls)` of them target an `output/` subdirectory that is not part of the deposit.
The archive ships no derived objects, so the stripped-copy test is vacuous here and is reported
as such rather than as a pass.

`r nrow(pass("as_shipped") |> filter(outcome != "clean"))` of
`r nrow(pass("as_shipped"))` scripts stop on an error, for four distinct reasons.

```{r}
#| label: archive-errors
#| echo: false
pass("as_shipped") |>
  filter(outcome != "clean") |>
  transmute(script, stopped_at = str_trunc(stopped_at, 60)) |>
  show_table(caption = "Where each failing script stopped, as shipped.")
```

- **Two scripts fail because the deposit does not ship the directory they write into.**
  `figure_3.R` calls `ggsave("output/figure_3.pdf", ...)` and `table_1.R` opens
  `output/table_1a.tex` for writing. Neither `output/` nor any `dir.create()` is in the deposit,
  so on a clean copy both stop at their first write. Every estimate each script computes is
  already in memory when it stops.
- **Two scripts fail on data files the deposit does not contain.** `figure_B1.R` reads
  `fielding_dates.rds` and `fielding_dates_survey.rds`; `figure_C4.R` reads
  `weekly_adds_for_page_id_disclaimer_041322.csv`. The deposit's own README lists all three among
  the files the appendix scripts depend on. They are the reason Supplementary Figures 1 and 4
  have no coverage here.
- **`figure_2.R` fails on a missing package.** It calls `xtable()` after opening with
  `rm(list = ls())` and without `library(xtable)`, so the call resolves only if a previous script
  attached the package in the same session.
- **`in_text_calculations.R` fails on a commented-out package.** Its `library(lmtest)` line is
  commented out and it calls `waldtest()`. Everything above that line runs.

**One further defect in the deposit is not visible as a failure**, because the script stops before
reaching it. Below the `waldtest()` call, `in_text_calculations.R` computes the article's six
advertising spending figures with `filter(!is_turnout)` and `group_by(ad_format)` and
`group_by(ad_type)`. The deposited `ad_library_2020_acronym.csv` carries none of those three
columns; they are built in `figure_B2.R`. So the script that is named for the in-text
calculations cannot produce the in-text spending figures even after the `lmtest` line is
restored. All six reproduce from `figure_B2.R`'s classification, which is what this rewrite uses.

Running the deposit in place would add `r nrow(overwrites |> filter(effect == "added"))` file to
the archive directory, an `Rplots.pdf` from the scripts that print a plot to the active device,
and would overwrite `r nrow(overwrites |> filter(effect == "overwritten"))` deposited files.

**The archive reproduces the article.** Every one of the
`r sum(coverage$reproduced_by_archive, na.rm = TRUE)` numbers the article's six large floats print
is recovered from the deposited code, and none of the `r sum(!is.na(gt$match))` ground truth rows
with an archive counterpart disagrees with the page.

## Errata

`r str_to_title(n_errata_word)` sentences in the published article are wrong, and they
are corrected in
[`aggarwal_etal_2023_errata.pdf`](aggarwal_etal_2023_errata.pdf), whose values are computed at
render time from this repository's output. None of them changes a conclusion. In summary: the
Supplementary Information names July as the month of heaviest persuasion spending where the
figure it points at makes it February, and that cross-reference does not resolve; the Methods
count 21 pre-treatment covariates where Figure 5 and Supplementary Table 3 both carry
`r value("methods_n_covariates")`; the treatment audience is given as
"`r with_commas(value("methods_treatment_audience"))` million" where the sentence's own
parenthetical makes it `r with_commas(value("methods_treatment_audience"))`; the balance F test's
degrees of freedom are printed as the residual count first and a negative parameter difference
second; and one share is rounded down where it rounds up.

### Findings that are not errata

**The deposited scripts are not quite the scripts that made the published figures.**
`figure_3.R` draws two `geom_label` annotations reading "Control group" and "Treatment group";
the published Figure 3 carries neither. `figure_5.R` labels its axis rows "Trump support score /
100", "Turnout score / 100", "Ideology score / 100" and "Partisanship score / 100"; the published
Figure 5 prints "TSS/100", "Turnout score/100", "Ideology score/100" and "Partisanship
score/100". Every estimate in both figures reproduces exactly. The rewrite follows the deposited
code, so its Figure 3 carries the two labels.

**One targeting criterion does not hold in the data the article analyses.** Figure 4 gives the
targeting criteria as a Trump support score between 30 and 70 and a presidential turnout score
between 20 and 80. The Trump support score in the deposited analysis set runs exactly
`r sprintf("%.0f", value("figure_4_tss_target_min"))` to
`r sprintf("%.0f", value("figure_4_tss_target_max"))`. The presidential turnout score runs
`r sprintf("%.1f", value("figure_4_pts_target_min"))` to
`r sprintf("%.1f", value("figure_4_pts_target_max"))`, so the upper half of the criterion is not
satisfied. The same figure states the archival subset's own criteria as a presidential turnout
score above 20 with no upper bound, and the analysis sample is that subset, so the two
descriptions in one figure are not consistent with each other. Which is right cannot be settled
from the deposit, and no published estimate depends on it, so this is recorded as unresolved
rather than corrected.

**The state list of the Facebook Ad Library query appears twice and differs.** Supplementary
Information section C describes the query as covering AZ, MI, NC, PA and WI; the caption of
Supplementary Figure 3, which that query produces, lists AZ, GA, MI, NC, PA and WI. The deposited
extract carries no state field, so neither list can be checked. The total the section states,
US\$`r with_commas(value("si_c_total_spend_all_advertisers"))`, is the lower-bound sum over the
whole deposited extract and reproduces exactly.

**The Reporting Summary gives the study's timing as July to November 2020** where the Methods
describe an eight-month programme running from March 2020 to election day. The Reporting Summary
form does not say which activity it is timing, so this is left as an inconsistency rather than
corrected.

**The registration date of the pre-analysis plan appears twice and differs.** Supplementary
Information section D says the plan was registered on 22 November 2020; the plan it reproduces is
dated 11 November 2020. A registration can postdate a document, so this is not necessarily an
error.

## The ground truth

`ground_truth/aggarwal_etal_2023_ground_truth.csv` carries one row per published claim, `r nrow(gt)`
of them. `value_paper` is the string the article prints and is the only column anyone typed;
`value_script` is read out of the deposited code and `value_rewrite` out of `maintained/output/`,
both by script. A value agrees when the computed number, printed to the page's own precision,
gives the same digits.

```{r}
#| label: gt-summary
#| echo: false
gt |>
  left_join(extraction |> select(claim_id, claim_type), by = "claim_id") |>
  mutate(verdict = case_when(
    !is.na(match_rewrite) & match_rewrite == 1 ~ "reproduces",
    !is.na(match_rewrite) & match_rewrite == 0 ~ "does not reproduce",
    !is.na(holds) & holds ~ "holds",
    !is.na(holds) & !holds ~ "does not hold",
    .default = "no verdict"
  )) |>
  count(claim_type, verdict) |>
  pivot_wider(names_from = verdict, values_from = n, values_fill = 0) |>
  show_table(caption = "Published claims by type and verdict.")
```

```{r}
#| label: gt-locus
#| echo: false
gt |>
  filter(!is.na(defect_locus)) |>
  count(defect_locus, name = "rows") |>
  show_table(caption = "Where the fault lies, on every row that is not a clean match.")
```

Every adverse row carries a `defect_locus` and no clean match carries one. The five values are
`paper_internal` (the article disagrees with its own tables or its own data), `archive` (the
deposit cannot support the claim), `environment` (R or a package moved underneath it), `rewrite`
(ours) and `unresolved` (cause not established). The `archive` rows here are almost all of one
kind: the deposit is the analysis subset and one Ad Library extract, and the article also
describes an assignment population of 31 million voters, a Facebook match rate, an impressions
count and a Wesleyan Media Project spending series, none of which the deposit was ever going to
carry.

### Coverage, float by float

```{r}
#| label: coverage
#| echo: false
coverage |>
  mutate(fraction = if_else(published_numbers > 0,
                            sprintf("%.0f%%", 100 * covered / published_numbers),
                            NA_character_)) |>
  select(float, `published numbers` = published_numbers, covered, fraction,
         `reproduced by rewrite` = reproduced_by_rewrite,
         `reproduced by archive` = reproduced_by_archive) |>
  show_table(caption = "Coverage per published float. Published numbers are what the float puts on its own face, or the countable quantities it asserts where it prints none.")
```

Six floats carry the bulk of the published record. Supplementary Tables 1, 2 and 3 print
`r nrow(appendix_cells)` numbers between them, main-text Table 1 prints
`r sum(maintext_cells$float == "table_1")`, and Figures 1 and 2 print an estimate and a standard
error above every point, `r sum(maintext_cells$float == "figure_1")` and
`r sum(maintext_cells$float == "figure_2")` numbers, which makes them published tables in
disguise. All `r published_numbers_total` are parsed from the published PDFs into
`ground_truth/published_appendix_values.csv` and
`ground_truth/published_maintext_tables.csv` and compared cell by cell. Every one reproduces.

Figures 1 and 2 are read positionally from the text layer, never in reading order, and they are
read from the figures themselves rather than from the supplementary tables their captions point
at. That makes the agreement between the two published transcriptions a finding: all
`r sum(maintext_cells$float == "figure_1" & maintext_cells$quantity %in% c("estimate", "se"))`
of Figure 1's cells and all
`r sum(maintext_cells$float == "figure_2" & maintext_cells$quantity %in% c("estimate", "se"))`
of Figure 2's equal the corresponding supplementary table cell.

Figures 3 and 5 print no numbers on their faces. For those the checkable published quantity is
what they plot: Figure 3 plots `r value("figure_3_points_plotted")` binned means, which is 41
one-point bins by two conditions by three outcomes, and Figure 5 plots
`r value("figure_5_points_plotted")` covariate estimates, one per axis label. Both counts are
verified and both figures' underlying estimates are written to CSV.

**Two floats have zero coverage and the reason is the same in both cases.** Supplementary Figure
1 needs `fielding_dates.rds` and `fielding_dates_survey.rds`; Supplementary Figure 4 needs
`weekly_adds_for_page_id_disclaimer_041322.csv`. None of the three is among the
`r nrow(manifest)` deposited files, the deposited scripts that read them fail at their first
read, and neither figure prints any number other than its axis breaks. Figure 6 is two
photographs of advertisements and asserts no quantity at all.

## The extraction and the two instruments

`ground_truth/published_claims.csv` is the extraction: `r nrow(extraction)` rows, one per
quantitative claim in the article, its figure captions, its Methods, its Reporting Summary and
its Supplementary Information, each classified by hand as `pipeline`, `descriptive`,
`definitional`, `structural` or `transcribed`, and each carrying the string the page prints and
the precision it prints it at.

```{r}
#| label: extraction
#| echo: false
extraction |>
  count(claim_type, needs_block) |>
  pivot_wider(names_from = needs_block, values_from = n, values_fill = 0,
              names_prefix = "needs a block: ") |>
  show_table(caption = "The extraction by claim type and whether the pipeline can reach the quantity.")
```

It was built by extracting every numeric token from the text layer of both PDFs with its
surrounding context, then classifying each by hand. Numbered citation markers, the reference
lists, calendar years used only as dates and the article's own DOI are excluded, and the six
floats above are carried as one row each with their cells compared separately rather than as
`r published_numbers_total` rows. A companion pass swept for numbers written as words, which no
token scan sees: "five battleground states", "8-month-long", "plus or minus one-third of a
percentage point", "only two exhibited statistically significant imbalance" and "greater than
three points" all entered the extraction that way.

Two instruments read the same pipeline output by separate paths.
`ground_truth/build_ground_truth.R` builds the comparison table. `maintained/in_text_claims.R`
carries the article's own sentence in a block comment beside code that recomputes the number, and
prints `r sum(extraction$needs_block)` claims in the form `CLAIM <id> = <value> || <label>`. It
reads `maintained/output/` and the extraction, never the ground truth, so the two derivations are
independent and a disagreement between them is a finding.

The build asserts all of the following and stops if any fails.

- Every `pipeline` and `descriptive` claim has a block and a row.
- Re-rendering `value_paper` from its own number at its own recorded precision returns the string
  the extraction stores. This runs before anything consumes the precision, because it is the
  check that catches a precision right about the value and wrong about the digits.
- Where the same published quantity is printed both in prose and in a supplementary table, the
  two hand transcriptions agree at whichever precision is coarser.
- The number of printed claims equals the number of rows requiring one, and the two sets of ids
  are equal in both directions.
- Every value the two instruments both produce agrees exactly.
- Every published cell joins to exactly one pipeline value; a published cell that finds nothing
  stops the build rather than becoming missing.
- Every adverse row carries a `defect_locus` and no clean match does.
- The ground truth and the extraction cover the same claims, in both directions.

Three of these were tested by breaking them, and the checks are ordered so that each break
reaches its own: deleting a block fails the count and the id comparison, perturbing a printed
value fails the cross-instrument comparison, and changing one claim's recorded precision fails
the string check before the value comparison can absorb it.

### What the second instrument found that a float-shaped ground truth would not

Every number in the article's six large floats reproduces, so a ground truth built around floats
would have returned a clean sweep. All `r n_errata_word` errata, and every finding above, are prose,
captions or the document's own structure.

```{r}
#| label: descriptive
#| echo: false
descriptive |>
  transmute(claim = str_trunc(statement, 90), holds) |>
  show_table(caption = "Descriptive claims: what the article asserts about shape, sign and count, and whether it holds. The evidence behind each verdict is written out beside it in the pipeline output.")
```

## The maintained rewrite

`maintained/` is `r length(list.files(here::here("maintained"), pattern = "\\.R$"))` scripts.
Every figure and table script writes the unrounded estimates it plots or prints alongside the
figure itself, so nothing downstream reads a number back out of a formatted cell.

The substitutions are the usual ones for code of this age: the native pipe for `magrittr`,
`reframe(tidy(...))` for `do(tidy(...))`, `pick(everything())` for the implicit `.` inside `do()`,
`if_else()` for `ifelse()`, `separate_wider_delim()` for `separate()`, `knitr::kable()` written to
a file for `xtable` printed through a connection, and `label_dollar()`/`label_date()` for the
`scales::` formatter aliases. `rm(list = ls())` is dropped, packages are loaded once in
`helpers.R`, and every path goes through `here::here()`.

**One property of the deposited data has to be handled explicitly.**
`aggregated_analysis_set.rds` is a grouped tibble, grouped by all 41 of its covariate columns,
which is what a `count()` leaves behind. A bare `summarize()` over it returns two million rows
rather than one, which is why the deposit's `table_1.R` calls `ungroup()` before its total row.
The rewrite drops the grouping when the file is read, where it cannot be forgotten.

**The rewrite adds three published tables the deposit computes and never writes.** The deposited
`figure_1.R`, `figure_2.R` and `figure_5.R` each assemble an `xtable` object holding exactly the
cells of Supplementary Tables 1, 2 and 3, and each has its `print.xtable()` call commented out.
Those three tables are `r nrow(appendix_cells)` of the article's published numbers, and without
writing them there is no artifact to compare against.

## Figure verification

Every rendered figure was laid beside the published one. Numbers alone cannot catch a transposed
axis or a mislabelled series, and two of this article's four plotted figures print their estimates
on the face of the plot.

```{r}
#| label: figure-1
#| echo: false
#| fig-cap: "Figure 1 as the rewrite draws it. All 114 printed labels, the facet order and the row order within each facet reproduce the published figure."
figure("figure_1_ate_cate_estimates")
```

```{r}
#| label: figure-2
#| echo: false
#| fig-cap: "Figure 2 as the rewrite draws it. All 36 printed labels reproduce."
figure("figure_2_heterogeneity_by_tss")
```

```{r}
#| label: figure-3
#| echo: false
#| fig-cap: "Figure 3 as the rewrite draws it. The two group labels come from the deposited script; the published figure does not carry them."
figure("figure_3_turnout_by_tss_score")
```

```{r}
#| label: figure-5
#| echo: false
#| fig-cap: "Figure 5 as the rewrite draws it, with the deposited script's own covariate labels."
figure("figure_5_balance")
```

```{r}
#| label: figure-b2
#| echo: false
#| fig-cap: "Supplementary Figure 2 as the rewrite draws it."
figure("figure_b2_acronym_spending")
```

```{r}
#| label: figure-c3
#| echo: false
#| fig-cap: "Supplementary Figure 3 as the rewrite draws it."
figure("figure_c3_facebook_spending")
```

## Rewrite verification

`run_all.R` was run to completion twice from clean sessions and the whole tree diffed. Every CSV
and TeX file is byte-identical between runs. The figure PDFs differ, because a PDF records the
time it was written.

`original/` is verified twice per run. `download_original.R` is sourced first, which checks every
file against the MD5 Dataverse serves for `?format=original` and against its deposited byte size,
and then refuses to continue if `original/` holds any file the manifest does not list, dotfiles
included. It is sourced again as the last step, because the first pass proves only that the
archive was intact when the run began. All `r nrow(manifest)` files match, and
`r sum(manifest$md5_served != manifest$md5_published)` carry a published checksum that disagrees
with the bytes Dataverse serves. Two of the sixteen are ingested as tabular data and are served
under a `.tab` name unless the original format is requested; the manifest records both names.
Checksums for files this repository writes are not quoted anywhere: a PDF records its write time,
so its hash changes on every run.

## R environment

```{r}
#| label: session
#| echo: false
tibble(
  component = c("R", "tidyverse", "estimatr", "car", "lmtest", "ggplot2"),
  version = c(
    paste(R.version$major, R.version$minor, sep = "."),
    as.character(packageVersion("tidyverse")),
    as.character(packageVersion("estimatr")),
    as.character(packageVersion("car")),
    as.character(packageVersion("lmtest")),
    as.character(packageVersion("ggplot2"))
  )
) |>
  show_table()
```

The article reports R 4.1.1 with tidyverse 1.3.1, estimatr 0.30.6 and car 3.1.0. Nothing in this
analysis draws at random: no script calls `sample()`, `rnorm()` or a bootstrap, so the results are
bit-identical at any seed and the sampler change in R 3.6 is not in play. The one place where
composing two packages could have moved a published number is the omnibus balance test, which
calls `lmtest::waldtest()` on two `estimatr::lm_robust` objects. Current `estimatr` exports a
`vcov` method that the version of the day did not, which is the mechanism that silently changed
an entire published table in another archive in this programme. Here it does not bite: the test
returns `r sprintf("%.4f", value("methods_omnibus_f"))` on
`r value("methods_omnibus_df_first_subscript")` and
`r with_commas(value("methods_omnibus_df_second_subscript"))` degrees of freedom, which is the
published statistic exactly.
